Robust Estimation, Prediction and Control with \\ Linear Dynamics and Arbitrary Costs

### 2020-01-20 main.tex
Update intro and algo

\begin{abstract}
	We study the adaptive control of a linear system with unknown parameters and arbitrary costs in a critical setting where failures are costly and should be prevented at all time. We build on two ideas. First, we incorporate prior knowledge of the dynamics in the form of a known structure of uncertainty, that can be tightened as we collect interaction data by building high-confidence regions through least-square regression. Second, we act in a cautious way with respect to this uncertainty by formulating a robust objective, that we solve approximately in a prediction-optimisation manner, leveraging tools from interval prediction and tree-based planning. Additionally, we relax our modelling assumptions by proposing an extension based on multi-model selection and aggregation. The full procedure is designed to produce reasonable and safe behaviour at deployment, get more aggressive with time, and be asymptotically optimal. We illustrate it on a practical case of autonomous driving at an intersection.
\end{abstract}

@@

@@

\begin{algorithm}[tb]
   \caption{Robust Estimation, Prediction and Control}
   \label{alg:full}
\begin{algorithmic}
   \STATE {\bfseries Input:} confidence level $\delta$
   \FOR{$N = 1,2,3,\dots$} 
   \STATE Compute the dynamics confidence region $\cC_{[N],\delta}$ with \textsc{Model Estimation} \eqref{eq:generic-polytope} on $\cD_{[N]}$.
   \FOR{planning steps $[T]$}
   \STATE Get the tree node $\bu^t$ to expand with \textsc{Pessimistic Planning}  \eqref{eq:surrogate_objective} using $[\underline{x}(t,\bu), \overline{x}(t,\bu)]$.
   \STATE For each child transition, simulate $[\underline{x}, \overline{x}]$ with \textsc{Interval Prediction} \eqref{eq:interval-predictor} using $\cC_{[N],\delta}$.
   \ENDFOR
   \STATE Execute the first recommended control $u_N$, and add the observed transition $(x_N, u_N, \dot{x}_N)$ to $\cD_{[N+1]}$.
   \ENDFOR

\end{algorithmic}
\end{algorithm}

>>>>

\begin{abstract}
	We develop a framework for the adaptive control of a linear system with unknown parameters and arbitrary costs in a critical setting where failures are costly and should be prevented at all time. We build on two ideas: first, we incorporate prior knowledge of the dynamics in the form of a known structure of the uncertainty, which can be tightened as we collect interaction data by building high-confidence regions through least-square regression. Second, we act in a cautious way with respect to this uncertainty by formulating a robust objective, that we solve approximately in a prediction-optimisation manner, leveraging tools from interval prediction and sequential planning literatures. Additionally, we relax our modelling assumptions by proposing an extension based on multi-model selection and aggregation. The full procedure is designed to produce reasonable and safe behaviour at deployment, get more aggressive with time, and be asymptotically optimal. We illustrate it on a practical case of autonomous driving at an intersection.
\end{abstract}

@@

Despite the dazzling successes of Reinforcement learning in cracking many problems considered unsolvable in the past decade [ref needed], this tool has hardly been applied in real industrial issues. This could be attributed to two undesirable properties which limit its practical applications: its dependence on a tremendous amount of interaction data that cannot always be simulated, and its reliance on trial-and-error and random exploration. In this paper, we consider the problem of controlling an unknown system in a critical setting where mistakes are costly and must be avoided at all time. Crucially, we wish to handle \emph{arbitrary} bounded reward functions $R$, for instance non-convex and non-smooth functions that naturally arise in problems

@@

\begin{algorithm}[tb]
   \caption{Robust Estimation, Prediction and Control (v1)}
   \label{alg:full}
\begin{algorithmic}
   \STATE {\bfseries Input:} confidence level $\delta$
   \FOR{$N = 1,2,3,\dots$} 
   \STATE Compute the dynamics confidence region $\cC_{[N],\delta}$ with \textsc{Model Estimation} \eqref{eq:generic-polytope} on $\cD_{[N]}$.
   \FOR{planning steps $k\in[K]$}
   \STATE Get the tree node $\bu_k$ to expand with \textsc{Pessimistic Planning}  \eqref{eq:opd} using $\underline{R_n}$ over $[\underline{x}_{n}, \overline{x}_{n}]$. \COMMENT{Selection}
   \STATE For each action, simulate the child transition $[\underline{x}_{n+1}, \overline{x}_{n+1}]$ with \textsc{Interval Prediction} \eqref{eq:interval-predictor} using $\cC_{[N],\delta}$. \COMMENT{Expansion}
   \ENDFOR
   \STATE Execute the first recommended control $u_N$, and add the observed transition $(x_N, u_N, \dot{x}_N)$ to $\cD_{[N+1]}$.
   \ENDFOR
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[tb]
	\caption{Robust Estimation, Prediction and Control (v2)}
	\begin{algorithmic}
		\STATE {\bfseries Input:} confidence level $\delta$
		\FOR{$N = 1,2,3,\dots$} 
		\STATE $\cC_{[N],\delta} \gets$\textsc{Model Estimation}$(\cD_{[N]})$. \eqref{eq:generic-polytope}
		\FOR{planning steps $k\in[K]$}
		\STATE $a_k\gets$\textsc{Pessimistic Planning}$(\underline{R_n}([\underline{x}_{n}, \overline{x}_{n}]))$.  \eqref{eq:opd}
		\FOR{$b\in A$}
		\STATE $[\underline{x}_{n+1}(a_k b), \overline{x}_{n+1}(a_k b)]\gets$ \textsc{Interval Prediction}($\cC_{[N],\delta}$). \eqref{eq:interval-predictor}
		\ENDFOR
		\ENDFOR
		\STATE Execute the first recommended control $u_N$, and add the observed transition $(x_N, u_N, \dot{x}_N)$ to $\cD_{[N+1]}$.
		\ENDFOR
	\end{algorithmic}
\end{algorithm}
